HEP Software Foundation Community White Paper Working Group -- Detector Simulation

### 2018-02-20 CWP/papers/HSF-CWP-2017-07_detsim/latex/DetectorSimulation.tex
updated author list
updated author and affiliation lists

\author[d]{J Apostolakis}
\author[q]{M Asai}
\author[n]{S Banerjee}
\author[m]{R Bianchi}
\author[d]{F Carminati}
\author[l]{R Cenci}
\author[b]{J Chapman}
\author[d]{G Corti}
\author[d]{G Cosmo}
\author[p]{S Easo}
\author[q]{A Dotti}
\author[f,1]{V Elvira}
\author[f]{L Fields}
\author[f]{K Genser}
\author[d]{A Gheata}
\author[d]{M Gheata}
\author[d]{I Goulas}
\author[d,1]{J Harvey}
\author[d]{F Hariri}
\author[f]{R Hatcher}
\author[f]{K Herner}
\author[d]{V Ivantchenko}
\author[f]{T Junk}
\author[f]{S-Y Jun}
\author[f]{M Kirby}
\author[f]{R Kutschke}
\author[f]{P Lebrun}
\author[f]{A Lyon}
\author[j]{Z Marshall}
\author[c]{J-F Marchand}
\author[a]{M Mooney}
\author[q]{R Mount}
\author[k]{J Mousseau}
\author[j]{B Nachman}
\author[f]{A Norman}
\author[f]{I Osborne}
\author[f]{K Pedro}
\author[d]{W Pokorski}
\author[a]{X Qian}
\author[f]{J Raaf}
\author[l]{M Rama}
\author[d]{A Ribon}
\author[d]{S Roiser}
\author[o]{D Ruterbories}
\author[f]{S Sekmen}
\author[h]{B Siddi}
\author[f]{E Snider}
\author[g]{S Vallecorsa}
\author[e]{M Verderi}
\author[f]{H Wenzel}
\author[d]{S Wenzel}
\author[d]{B Viren}
\author[f]{T Yang}
\author[f]{L Welty-Rieger}

@@

\affiliation[a]{Brookhaven National Laboratory, Upton NY, USA}
\affiliation[b]{University of Cambridge,Cambridge, UK}
\affiliation[c]{Carleton University, Ottawa, ON, Canada}
\affiliation[d]{CERN, Geneva, Switzerland}
\affiliation[e]{IN2P3-LLR, Ecole Polytechnique, Palaiseau, France}
\affiliation[f]{Fermilab National Accelerator Laboratory, Batavia IL , USA}
\affiliation[g]{Gangneung-Wonju National University, Gangneung, Gangwon-do, South Korea}
\affiliation[h]{Università di Ferrara and INFN Ferrara, Ferrara, Italy}
\affiliation[j]{Lawrence Berkeley National Laboratory, Berkeley CA, USA}
\affiliation[k]{University of Michigan, Ann Arbor MI, USA}
\affiliation[l]{Università di Pisa and INFN Pisa, Pisa, Italy}
\affiliation[m]{University of Pittsburgh, Pittsburgh PA, USA}
\affiliation[n]{Princeton University, Princeton, NJ 08544, USA}
\affiliation[o]{University of Rochester, Rochester NY, USA}
\affiliation[p]{Rutherford Appleton Laboratory, Chilton, UK}
\affiliation[q]{SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA}
\affiliation[r]{University of Illinois Urbana-Champaign, Champaign IL, USA}

\affiliation[1]{Paper Editor}

>>>>

\author[c]{J Apostolakis}
\author[p]{M Asai}
\author[e]{S Banerjee}
\author[l]{R Bianchi}
\author[e]{P Canal}
\author[k]{R Cenci}
\author[b]{J Chapman}
\author[c]{G Corti}
\author[c]{G Cosmo}
\author[o]{S Easo}
\author[h]{L de Oliveira}
\author[p]{A Dotti}
\author[e,1]{V Elvira}
\author[e]{L Fields}
\author[e]{K Genser}
\author[c]{A Gheata}
\author[c]{M Gheata}
\author[c,1]{J Harvey}
\author[c]{F Hariri}
\author[e]{R Hatcher}
\author[e]{K Herner}
\author[j]{M Hildreth}
\author[c]{V Ivantchenko}
\author[e]{T Junk}
\author[e]{S-Y Jun}
\author[e]{M Kirby}
\author[m]{D Konstantinov}
\author[e]{R Kutschke}
\author[e]{P Lebrun}
\author[e]{G Lima}
\author[e]{A Lyon}
\author[h]{Z Marshall}
\author[c]{P Mato}
\author[a]{M Mooney}
\author[p]{R Mount}
\author[i]{J Mousseau}
\author[h]{B Nachman}
\author[e]{A Norman}
\author[c]{M Novak}
\author[e]{I Osborne}
\author[q]{M Paganini}
\author[e]{K Pedro}
\author[c]{W Pokorski}
\author[a]{X Qian}
\author[k]{M Rama}
\author[c]{A Ribon}
\author[c]{S Roiser}
\author[n]{D Ruterbories}
\author[e]{S Sekmen}
\author[g]{B Siddi}
\author[e]{E Snider}
\author[f]{S Vallecorsa}
\author[d]{M Verderi}
\author[e]{H Wenzel}
\author[c]{S Wenzel}
\author[a]{B Viren}
\author[e]{T Yang}
\author[e]{J Yarba}
\author[e]{L Welty-Rieger}

@@

\affiliation[a]{Brookhaven National Laboratory, Upton NY, USA}
\affiliation[b]{University of Cambridge,Cambridge, UK}
\affiliation[c]{CERN, Geneva, Switzerland}
\affiliation[d]{IN2P3-LLR, Ecole Polytechnique, Palaiseau, France}
\affiliation[e]{Fermilab National Accelerator Laboratory, Batavia IL , USA}
\affiliation[f]{Gangneung-Wonju National University, Gangneung, Gangwon-do, South Korea}
\affiliation[g]{Università di Ferrara and INFN Ferrara, Ferrara, Italy}
\affiliation[h]{Lawrence Berkeley National Laboratory, Berkeley CA, USA}
\affiliation[i]{University of Michigan, Ann Arbor MI, USA}
\affiliation[j]{University of Notre Dame, Notre Dame, IN 46556, USA}
\affiliation[k]{Università di Pisa and INFN Pisa, Pisa, Italy}
\affiliation[l]{University of Pittsburgh, Pittsburgh PA, USA}
\affiliation[m]{Institute For High Energy Physics(IHEP), Protvino,Russia}
\affiliation[n]{University of Rochester, Rochester NY, USA}
\affiliation[o]{Rutherford Appleton Laboratory, Chilton, UK}
\affiliation[p]{SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA}
\affiliation[q]{Yale University, New Haven, CT 06520, USA}
\affiliation[1]{Paper Editor}
